---
title: "Privitera et. al 2023 - Analysis of Figure 4 and related Figures"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# required libraries

```{r, echo=FALSE}
library(edgeR)
library(SummarizedExperiment)
library(SEtools)
library(plgINS)
library(ggplot2)
library(DESeq2)
library(sva)
library(cowplot)
library(dplyr)
library(xlsx)
library(sechm)
library(topGO)
library(GOplot)
source("../19122022_Figure4_Analysis/Functions.R")
set.seed(123)
sessionInfo()

```

# Load SE data

```{r}
TimeFST <- readRDS("../19122022_Figure4_Analysis/Data/TimeSeriesFST.SE.rds")
CSI1 <- readRDS("../19122022_Figure4_Analysis/Data/CSI1.SE.rds")
snSEQ <- readRDS("../19122022_Figure4_Analysis/Data/snRNAseq.SE.rds")
se <- readRDS("../19122022_Figure4_Analysis/Data/AstroTRAP_Ncom.SE.rds")
```

# Figure 4b,d,f: A deeper look at target genes across published data sets (Floriou-Servou et. al 2018, von Ziegler et. al 2022)

```{r}

t4 <- c("Dio2", "Ppp1r3c", "Ppp1r3g", "Sik1", "Nr4a1")


pCSI1 <- meltSE_LvZ(CSI1,t4, assays = "corrected")
Fig4b <- BoxplotMP(pCSI1,Condition2, value, Condition) + 
  scale_color_manual(values=c("grey18", "purple", "firebrick", "darkgreen", "orange")) +
  facet_grid(feature~Region, scales = "free") + 
  ylab("Relative expression")

Fig4b

pTimeFST <-meltSE_LvZ(TimeFST,t4, assays = "corrected")
Fig4d <- BoxplotMP(pTimeFST,Condition2, value, Condition2) +
      scale_color_manual(values=c("grey18", "firebrick", "grey30", "purple", "royalblue", "palegreen4")) +
      facet_grid(feature~Region, scales = "free") +
       ylab("Relative expression")

Fig4d


psnSEQ <- meltSE_LvZ(snSEQ,t4, assays = "logcpm")
psnSEQ2 <- subset(psnSEQ, cluster == 'Astrocytes' | cluster =='Excitatory\nNeurons' | cluster =='Inhibitory\nNeurons' | cluster =='Oligodendrocytes' | cluster =='Vascular')

Fig4f <- BoxplotMP(psnSEQ2, cluster, value, condition) + 
  scale_color_manual(values=c("grey18", "firebrick")) +
  facet_grid(~feature, scales = "free") + 
  ylab("logcpm")


Fig4f

```



#Figure 4h: Analysis of AstroTrap dataset (GSE126172) published by Murphy-Royal et. al 2020

## Statistical analysis of all genes

Analyse TRAP data by comparing expression between stressed and control mice

```{r}

se_TRAP <- se[,se$SampleProcessing == "Astro-TRAP"]

Results <- list()

y <- DGEList(counts = assays(se_TRAP)$counts,group = se_TRAP$Condition)
y <- calcNormFactors(y)
y <- estimateDisp(y)
y <- y[filterByExpr(y,group = se_TRAP$Condition),]
Results[["AllGenes"]] <- exactTest(y)

#sig_genes <- rownames(topTags(Results[["AllGenes"]]))

#VolcanoPlotsEdgeR(Results, lab = sig_genes)

test <- SEtools::meltSE(se_TRAP,"Dio2")
```

## Statistical analysis of target genes

TGs: Dio2, Ppp1r3c, Ppp1r3g und Sik1

```{r}
se_selection <- se_TRAP
targets <- c("Dio2", "Ppp1r3c","Ppp1r3g", "Sik1")

y <- DGEList(counts = assays(se_selection)$counts,group = se_selection$Condition)
y <- calcNormFactors(y) # 
y <- estimateDisp(y)
y <- y[c("Dio2", "Ppp1r3c","Ppp1r3g", "Sik1"),]

y <- y[filterByExpr(y,group = se_selection$Condition),]
Results[["OnlySelectedGenes"]] <- exactTest(y)
Results[["OnlySelectedGenes"]]
topTags(Results[["OnlySelectedGenes"]])

# Andere Variante wäre:
topTags(Results[["AllGenes"]][targets,])
```

Create boxplots

```{r}

pdat3 <- SEtools::meltSE(se_TRAP, genes = "Dio2")
A1 <- BoxplotMP(pdat3, Condition, logcpm, Condition) +
   scale_color_manual(values= c("grey18","firebrick"))+

  facet_grid(~feature, scales = "free")

pdat4 <- SEtools::meltSE(se_TRAP, genes = "Ppp1r3c")
A2 <- BoxplotMP(pdat4, Condition, logcpm, Condition) +
   scale_color_manual(values= c("grey18","firebrick"))+

  facet_grid(~feature, scales = "free")

pdat5 <- SEtools::meltSE(se_TRAP, genes = "Ppp1r3g")
A3 <- BoxplotMP(pdat5, Condition, logcpm, Condition) +
   scale_color_manual(values= c("grey18","firebrick"))+

  facet_grid(~feature, scales = "free")

pdat6 <- SEtools::meltSE(se_TRAP, genes = "Sik1")
A4 <- BoxplotMP(pdat6, Condition, logcpm, Condition) +
   scale_color_manual(values= c("grey18","firebrick"))+

  facet_grid(~feature, scales = "free")

Fig4h <- plot_grid(A1,A2,A3,A4,nrow = 1,rel_widths = c(1,1,1,1)) 

Fig4h

```



#Export figures

```{r}
pdf(file="../19122022_Figure4_Analysis/Figures/Fig4.pdf", width = 24, height=12)
print(Fig4b)
dev.off()
```

```{r}
pdf(file="../19122022_Figure4_Analysis/Figures/Fig4.pdf", width = 24, height=12)
print(Fig4d)
dev.off()
```

```{r}
pdf(file="../19122022_Figure4_Analysis/Figures/Fig4.pdf", width = 24, height=12)
print(Fig4f)
dev.off()
```

```{r}
pdf(file = "../19122022_Figure4_Analysis/Figures/Fig4h.pdf", width = 6, height = 4)
print(Fig4h)
dev.off()
```
